\section{Introduction}
One of quantum computing's most significant results is the development of Grover's
algorithm~\cite{bib-grover1996fast}. This algorithm performs an unstructured search
optimally~\cite{bib-zaika-grov-opt}. Various applications have
been proposed for such an algorithm, including the acceleration of solving NP-hard
problems~\cite{bib-williams-grover-np}.

Grover's algorithm uses a phase oracle, a quantum circuit that applies a phase of
$-1$ when the Boolean function it implements is true, to mark search hits in the
database.

It has been known that a restricted class of phase oracles can be implemented
using only phase gates such as the T, T$^\dagger$, as well as CNOT gates (hereafter
referred to as CNOT+T). In fact, phase oracles of 3 or fewer variables can all be
implemented exactly using this set of gates~\cite{bib-amy-cnot}, and these circuits
can be calculated exactly using the Boolean Fourier transform. These classes of
circuits are interesting because the T-gates and CNOT gates in them can be freely rearranged
to create equivalent circuits with lower T-depth. Selinger~\cite{bib-selinger-tdepthone}
demonstrated that with sufficient ancilla, many of them can be implemented in a
T-depth of one. Amy et al.~\cite{amy-meet-in-middle} further demonstrate that CNOT+T
circuits can be provably optimized for T-depth for a particular ancilla
count, in polynomial time~\cite{bib-amy-matroid}.

However, the vast majority of Boolean functions of 4 or more variables cannot be
implemented using only this gate set~\cite{bib-amy-rm}. There will inevitably be a need to use
a Hadamard (H) gate. The addition of this gate adds rotations that CNOT+T optimization
methods cannot account for. This means that methods to optimize for T-count and T-depth when
including the H gate are only heuristic~\cite{amy-meet-in-middle,bib-amy-matroid,bib-amy-rm}.
This renders any solution they have as either non-unique, or does not guarantee arrival
at a global minimum.

Existing oracle generation methods focus on driving a Boolean function on a single qubit's
state~\cite{bib-meuli-mult}. It is straightforward to implement a phase oracle from one of
these circuits by having them drive a Z gate on the qubit where the function is implemented,
and then implementing it again to return the state. However, as we will see later, these
types of constructions provide an obstacle to optimizing their T-depth, owing to their use
of Hadamard gates.

Instead, some phase oracle generation methods take advantage of the fact that
phase oracles are straightforward to synthesize from an Exclusive Sum
of Products (ESOP) expression~\cite{bib-phaseoracle}. Since each product term maps to
a Boolean function, it is easy to see that any such function expressible with
cubes of at most 3 variables can be implemented as a CNOT+T circuit. We utilize
this observation in our proposal.

In this work, we propose a solution that utilizes CNOT+T circuits to reduce the
T-count and T-depth for phase oracles of a given Boolean function of arbitrary
literal count.

Our contributions include:

\begin{itemize}
\item A precomputed library of circuits that implement all Boolean functions of
  3 variables or fewer.
\item A synthesis method that uses ESOP minimization to limit the number of
  product terms involving 4 or more variables.
\end{itemize}

We find that our solution can reduce T-count and T-depth by an average of 36.5\%
and over 65\% in some cases. We examine those cases and which ones the method
is best suited for.DCTODO

The rest of this paper is structured as follows: First Sec~\ref{Pre}
introduces some preliminary knowledge. In addition to the basics of
qubits and quantum circuits, this includes the basics of the
mathematics of phase polynomials and their mapping to phase oracles
and CNOT+T circuits. Then Sec.~\ref{Mot} goes through some
motivational examples that inform the general idea of our proposal.
Sec.~\ref{Pro} details the proposal itself, including how to
generate a library of up to 3-qubit phase oracles, and how to use
it to generate phase oracles of 4 or more qubits. In Sec.~\ref{Exp},
we test our results against Qiskit PhaseOracle and analyze our
findings. Finally, Sec.~\ref{Conc} concludes with our findings and
proposes some future research.

