\documentclass[conference]{IEEEtran}

\usepackage{multirow}
\usepackage{float}
\usepackage{cite}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{amsmath,amssymb,amsfonts,amstext}
% \usepackage{algorithmic}
\usepackage[dvipdfmx]{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{colortbl}
\usepackage[T1]{fontenc}
\usepackage{mdframed}
\usepackage{algorithm, algpseudocode} % texlive-science
\usepackage[braket, qm]{qcircuit}
\usepackage{newtxtext}
\usepackage[normalem]{ulem}
\usepackage{nameref}
\usepackage{tikz}
\usetikzlibrary{arrows.meta, shapes, positioning, calc, fit}

\input{img/defs}

\makeatletter
\newcommand{\sublabel}[1]{\protected@edef\@currentlabel{\thefigure(\thesubfigure)}\label{#1}}
\makeatother
\captionsetup{subrefformat=parens}
\algrenewcommand\algorithmicindent{0.5em}
\newtheorem{definition}{Definition}
\newtheorem{example}{Example}
\newcommand{\thickhline}{%
    \noalign {\ifnum 0=`}\fi \hrule height 1pt
    \futurelet \reserved@a \@xhline
}
%\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
%    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\newcommand{\figcaption}[1]{\def\@captype{figure}\caption{#1}}
\newcommand{\tblcaption}[1]{\def\@captype{table}\caption{#1}}

\newcommand{\Del}[1]{\textcolor{red}{\sout{#1}}}
\newcommand{\Add}[1]{\textcolor{blue}{\emph{#1}}}

\newcount\NGCcolor
\NGCcolor=1
\newcount\NGCcolortwo
\NGCcolortwo=1
%\NGCcolor=0
\ifnum\NGCcolortwo<1
  \newcommand{\blueoutt}[1]{\textcolor{blue}{#1}}  
\else
  \newcommand{\blueoutt}[1]{#1}
\fi
  
\ifnum\NGCcolor<1
  \newcommand{\redout}[1]{\textcolor{red}{#1}}
  \newcommand{\blueout}[1]{\textcolor{blue}{#1}}
  \newcommand{\greenout}[1]{\textcolor{green}{#1}}
  \newcommand{\cyannout}[1]{\textcolor{cyan}{#1}}
  \newcommand{\magentaout}[1]{\textcolor{magenta}{#1}}
  \newcommand{\yellowout}[1]{\textcolor{yellow}{\bf #1}}
  \newcommand{\algblueout}[1]{\leavevmode\color{blue}{#1}}
\else
  \newcommand{\redout}[1]{#1}
  \newcommand{\blueout}[1]{#1}
  \newcommand{\greenout}[1]{#1}
  \newcommand{\cyannout}[1]{#1}
  \newcommand{\magentaout}[1]{#1}
  \newcommand{\yellowout}[1]{#1}
  \newcommand{\algblueout}[1]{\leavevmode {#1}}
\fi


% refs for section
\newcommand{\secref}[1]{Sec.~\ref{#1}}
\newcommand{\figref}[1]{Fig.~\ref{#1}}
\newcommand{\tabref}[1]{Table~\ref{#1}}
\newcommand{\eqnref}[1]{(\ref{#1})}

\begin{document}

\title{Synthesis of Phase Oracles Using CNOT+T Circuits and ESOP Minimization}
\author{
    \IEEEauthorblockN{\phantom{David Clarino}}
    \IEEEauthorblockA{\phantom{Ritsumeikan University} \\
      \phantom{dclarino@fc.ritsumei.ac.jp}}
    \and 
    \IEEEauthorblockN{\phantom{Chitranshu Arya}}
    \IEEEauthorblockA{\phantom{Netaji Subhas} \\
      \phantom{University of Technology} \\
      \phantom{chitranshu.arya.ug22@nsut.ac.in}}
    \and
    \IEEEauthorblockN{\phantom{Shigeru Yamashita}}
    \IEEEauthorblockA{\phantom{Ritsumeikan University} \\
      \phantom{ger@cs.ritsumei.ac.jp}}
    \and
    \IEEEauthorblockN{\phantom{Zanhe Qi}}
    \IEEEauthorblockA{\phantom{Ritsumeikan University} \\ \phantom{goose@ngc.is.ritsumei.ac.jp}}
}
%% \author{
%%     \IEEEauthorblockN{David Clarino}
%%     \IEEEauthorblockA{Ritsumeikan University \\
%%       dclarino@fc.ritsumei.ac.jp}
%%     \and 
%%     \IEEEauthorblockN{Chitranshu Arya}
%%     \IEEEauthorblockA{Netaji Subhas \\
%%       University of Technology \\
%%       chitranshu.arya.ug22@nsut.ac.in}
%%     \and
%%     \IEEEauthorblockN{Shigeru Yamashita}
%%     \IEEEauthorblockA{Ritsumeikan University \\
%%       ger@cs.ritsumei.ac.jp}
%%     \and
%%     \IEEEauthorblockN{Zanhe Qi}
%%     \IEEEauthorblockA{Ritsumeikan University \\
%%       goose@ngc.is.ritsumei.ac.jp}
%% }

\maketitle

\begin{abstract}
  Phase oracles are essential components of quantum algorithms such as Grover's algorithm. These circuits apply a phase of $-1$ to an input state when a particular Boolean function $f$ is true. In fault-tolerant quantum computing,there is a need to optimize the number of T-gates, known as the T-count, as well as the longest chain of such T-gates, known as the T-depth. A class of phase oracles implementable using only CNOT and T/T$^{\dagger}$ gates (the CNOT+T set) is well known to be conducive to optimization for T-count and T-depth, including provable, efficient optimization for a given number of qubits. However, in general, a universal gate set that includes the Hadamard gate is difficult to optimize, and many such T-count/T-depth optimization techniques have to work around them in the general case. We demonstrate that several standard ways of constructing such phase oracles are not conducive to optimization techniques such as T-par. In this work, we propose a way of synthesizing phase oracles that facilitates such optimization techniques. To construct a phase oracle that can be better optimized by these techniques, we attempt to express as much of it as possible as a CNOT+T circuit. To do this, we utilize the observation that Boolean functions of 3 or fewer variables can be implemented entirely using CNOT+T gates, ESOP generation of phase oracles such as used by Qiskit's \texttt{PhaseOracle}, and ESOP optimization to minimize the number of product terms over 3 variables. We compare the results against Qiskit's \texttt{PhaseOracle} method and find T-par can optimize such circuits with on average 36.5\% lower T-count and T-depth, and as much as 65\% in some cases.

%%   this class of circuits can be provably optimized for T-count and T-depth. We identify a class of Boolean functions of 4 or more variables which can be synthesized using such a circuit, by way of a library of circuits that implement phase oracles of 3 or fewer variables. We then use this to synthesize Boolean functions of 4 or more variables, by minimizing the number of ESOP terms of more than 3 variables and using a library of CNOT+T 3 variable circuits to synthesize cubes of 3 or fewer. This ensures as much of the circuit is implemented using only CNOT+T as possible and can thus be optimized by CNOT+T algorithms such as Tpar. 

%%   For functions of 3 or fewer variables, phase oracles are well known to be exactly implementable using only the CNOT, T, and T$^\dagger$ gates. 
\end{abstract}

\input{Intro}

\input{Pre}

\input{Mot}

\input{Pro}

\input{Exp}

\input{Conc}

% DCTODO: Add Evaluation, Results, and Conclusion Sections

\bibliographystyle{unsrt}
\bibliography{ref}

\end{document}
